\documentclass[12pt, a4paper]{report}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{ngerman}
\usepackage[left=2cm,top=2cm,right=2cm,bottom=2cm]{geometry}
\usepackage{charter}
\usepackage{tikz}
\usepackage{tcolorbox}
\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}

\newenvironment{gblock}[1]{
    \tcolorbox[beamer,
        noparskip,
        colback=green!75!,
        colbacklower=green!75!green,
        title=#1]}
{\endtcolorbox}

\newcommand{\friend}[0]{\texttt{Friend}}
\newcommand{\friendn}[0]{\friend\ }
\newcommand{\me}[0]{\texttt{Ben Siebert}}

\begin{document}
	\begin{gblock}{Subject: \texttt{RE: Would the Germans like a king or a Queen?} \\ To: \texttt{my-friend@english-class.co.uk}}
		Dear \friend, \\
		I was very happy hearing from you.
		The question you asked is a very interesting one on which I have read an article not too long ago. \\
		The Royals fulfill many longings of the Germans.
		The Germans long for cultural unity and want to feel more connected to each other.
		Beside that the Germans also love the idea of fairy tales.
		In fact almost every german fairy tale includes royalty.
		Germans admire the special rights that the royal family in England has. 
		The patriotism  also very high appreciated in Germany and they really like celebrations like royal weddings.
		In my opinion the Germans in general would love the idea of a german queen or king.
		But I do not think that a monarch with political rights would work out this well, because of how high Germans value the democracy in their land.
		\\
		Best Regards, \\
		\me
	\end{gblock}
\end{document}