\documentclass[12pt,a4paper]{report}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage{ngerman}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\newcommand{\fe}[0]{for example\ }
\newcommand{\lk}[0]{like\ }

\begin{document}
	\noindent
	\Large
	\textbf{Is education the ultimate driving force for social progress?}
	\large
	\\
	Charles Yidan said that \dq Education is the ultimate driving force for social progress\dq\ which I think is absolutely right. 
	The social progress includes many different aspects:
	\begin{itemize}
		\item making things better for the society,
		\item improving living conditions / lives / opportunities for everyone,
		\item and happier and more fulfilling lives.
	\end{itemize}
	The social progress is measured with the social progress index which includes all basic human needs like nutrition, a shelter and health care.
	I think that those goals are only achievable with the right education.
	It is just not possible to provide \fe health care without the proper education in the field of medicine.
	\\
	In my opinion education teaches the basic things you need in life and helps you integrate into the society.
	It teaches you how to talk properly, how to write properly and how to communicate with other people which is essential to live together with other people. \\
	Without education there wouldn't be experts in any field which would make it impossible to create a sustainable society in which everybody has a happier and more fulfilling live.
	We would not be able to improve the living conditions or the opportunities for everyone without these experts.
\end{document}